Re-run, Repeat, Reproduce, Reuse, Replicate:\\Transforming Code into Scientific Contributions

### 2017-08-24 draft.tex
update to latest random-walk codes

x = 0
for i in xrange(10):
    if random.uniform(-1, +1) > 0:
        x += 1
    else:
        x -= 1
    print x,
\end{code}
\end{minipage}

@@

x =  0
walk = []
for i in range(10):
    if random.uniform(-1, +1) > 0:
        x += 1
    else:
        x -= 1
    walk.append(x)

@@

random.seed(0) # RNG initialization

x =  0
walk = []
for i in range(10):
    if random.uniform(-1, +1) > 0:
        x += 1
    else:
        x -= 1
    walk.append(x)

@@

def generate_walk():
    walk = []
    x = 0
    for i in range(10):
        if random.uniform(-1, +1) > 0:
            x += 1
        else:
            x -= 1
        walk.append(x)
    return walk

>>>>

x = 0
for i in xrange(10):
    step = random.choice([-1,+1])
    x += step
    print x,
\end{code}
\end{minipage}

@@

x =  0
walk = []
for i in range(10):
    step = random.choice([-1,+1])
    x += step
    walk.append(x)

@@

random.seed(1) # RNG initialization

x =  0
walk = []
for i in range(10):
    step = random.choice([-1,+1])
    x += step
    walk.append(x)

@@

def generate_walk():
    x = 0
    walk = []
    for i in range(10):
        if random.uniform(-1, +1) > 0:
            x += 1
        else:
            x -= 1
        walk.append(x)
    return walk
